Momentum Strategy
========================================================

This about momentum strategy.  It is taken from [Ross Bennett's blog](http://rbresearch.wordpress.com/2012/08/23/momentum-with-r-part-1/)  

```{r, prepare, warning=FALSE, error = FALSE, message = FALSE}
require(quantstrat)

#Load ETFs from yahoo
currency("USD")
symbols = c("XLY", "XLP", "XLE", "XLF")
stock(symbols, currency="USD",multiplier=1)
getSymbols(symbols, src='yahoo', index.class=c("POSIXt","POSIXct"), 
           from='2000-01-01')
#Convert to monthly and drop all columns except Adjusted Close
for(symbol in symbols) {
  x <- get(symbol)
  x <- to.monthly(x,indexAt='lastof',drop.time=TRUE)
  indexFormat(x) <- '%Y-%m-%d'
  colnames(x) <- gsub("x",symbol,colnames(x))
  x <- x[,6] #drops all columns except Adjusted Close which is 6th column
  assign(symbol,x)
}
```
There are now four objects that have an adjusted close.Merge the symbols into a single object with just the close prices
```{r, merge}
symbols_close <- do.call(merge, lapply(symbols, get))
head(symbols_close)                   
```
Now calculate the three period rate of change so that the returns can be ranked ot see where the momentum lies. 
```{r, roc}
roc <- ROC(symbols_close, n = 3, type = 'discrete')
head(roc)
```
Now apply the rank function across each column. The symbol with the highest return has the rank one for each month. This will be an xts object with ranks. 
```{r, rank}
r <- as.xts(t(apply(-roc, 1, rank)))
head(r)
```


